Millions of Type Errors

### 2023-09-04 programming23/paper.tex
server timestamp less useful than client timestamp

Deduplicated records with the same client timestamp,
kept only the first.
Timestamps by millisecond.

Edit range ignore huge numbers (above 4B),
which are the result of subtraction overflowing.
%% 4,000,000,000

@@

%% TODO explain timestamps in prose, fig in appendix?

@@

%% TODO overall stats on type errors

>>>>

Deduplicated records with the same timestamp,
kept only the first.
Timestamps by millisecond.

Records come with two timestamps, a \emph{client timestamp}
that the IDE generates before sending the record
and a \emph{server timestamp} that the telemetry server
generates when it receives the record.
We collected timestamps to sort records from earliest to latest.
The server timestamps, however, are less useful for sorting
because the server processes groups of records in a batch and
often assigns equal timestamps to dozens of records.
Hence, we ignore the server timestamps.
Throughout the paper a \emph{timestamp} is always a client-side timestamp.

Edit range ignore huge numbers (above 4 billion),
which are the result of subtraction overflowing.
%% 4,000,000,000

@@

@@

%% results 1 section?!

%% TODO counting stats on type errors
%% - specific errors
%% - typos vs rest
%% - too complex
%% - mod switch vs other
